Evaluating the Effects of Tracker Reliability and Field of View on a Target Following Task in Augmented Reality

### 2009-06-25 trunk/Paper/paper.tex
changed a little more

From this plot we can see that with a small field of view, performance is equally bad with no dropouts or one second dropouts.  The small field of view seems to have a dominating effect on performance.  When the field of view is increased to the medium level, performance dramatically increases when there are no dropouts, but only gets slightly better when there are dropouts.  Finally, we do not observe much difference in performance between the medium and large field of view cases.  Using Tukey's HSD to compare means, the medium and large field of view conditions are in fact not significantly different ($p=0.575$).

>>>>

From this plot we can see that with a small field of view, performance is equally bad with no dropouts or one second dropouts.  
%The small field of view seems to have a dominating effect on performance.  
When the field of view is increased to the medium level, performance dramatically increases when there are no dropouts, but only gets slightly better when there are dropouts.  Finally, there is not a significant difference in performance between the medium and large field of view ($p=0.575$), which suggests that the medium field of view is enough for good performance.
%Finally, we do not observe much difference in performance between the medium and large field of view cases.  Using Tukey's HSD to compare means, the medium and large field of view conditions are in fact not significantly different ($p=0.575$).
